### 2018-11-07 Dissertation/Thesis.tex
complete draft of disertation

% =================================================================Abstract
\setlinespacing{2}
\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.
%
\vspace{5cm}
\\
\textbf{keywords}:  
	major depressive disorder, ensemble classification technique, supervised learning, psychological knowledge base.

@@

Major depressive disorder also known simply as depression,  is a global challenge for healthcare. In psychological domain, it is defined as a mental disorder consistent with at least two weeks of developing low mood across most situations \cite{Zimmerman}. Major depressive disorder can be successfully diagnosed by interviewers normally psychologists, applying operational diagnostic criteria of depression. However, a wide range of depressive patients did not seek clinic advices or professional care at all \cite{Huerta-Ramirez}. Health professionals hence often fail to approach a proper depressive patient at an early stage. 
\\

@@

Therefore, the objective of the present paper is to propose a suitable effective machine learning method in discriminating depression from collected health data for further interview diagnosis. 
\\
\bigskip
\goodbreak
% =================================================================Related-work
\section{Related Work}
\subsection{Psychological Studies Of Clarifying Depression}
In the domain of psychology, researchers created questionnaire-based scale instruments for roughly screening the mental status of patients. Several measures among them have been widely accepted as good and reliable tools, such as BDI \cite{Huerta-Ramirez}\cite{Tsugawa}, CES-D \cite{De Choudhury}\cite{Tsugawa}, SCL-20 and PHQ-9 \cite{Kroenke}. 
\\

@@

From these two studies on extracting depressive features, the task that aims at establishing a suitable dataset from online social media to predict depression based on extracted features is actually intricate. And there is a lack of machine learning methodology in these researches to automate the proceeding of classifying depression from non-depression.
\\
\medskip
\subsection{Research Of Classifying Depression On Social Media}
From various online contents of depressive symptoms and non-depression indicators, it is possible to use machine learning techniques to develop automatic detection systems for major depressive disorders. Unusual actions and uncommon patterns of interaction \cite{Wongkoblap} in social networks can be classified into cases or non-cases of depression through existing learning algorithms,  such as Support Vector Machine algorithm, Naive Bayes method and Random Forest technique.
\\

@@

Despite an increasing number of studies investigating depression using social media data, some common problems persist \cite{Wongkoblap}. Successfully distinguishing depressive users from rich­ data source like social media is problematic, "not only due to biases associated with the collection methods, but also with regard to managing consent and selecting appropriate analytics techniques" \cite{Wongkoblap}. In order to improve the performance of preliminary screening major depressive disorders in a relatively large samples, we need to explore a more suitable and high-quality classification technique for detecting depression.
\\
\bigskip
\goodbreak
% =================================================================Research Problem
\section{Research Problem}
This research aims to design an effective classification method for automatically detecting depressive risk of users in health data and is also able to potentially expend the model to be implemented in the real environment of social networks. 
\\

In order to clearly describe the research, the research objective is defined:\\\\
\textbf{Definition 1} \textit{Let $\mathbb{S}$ be a set of user properties to present an effective user profile for depression, a user property s $\in$ $\mathbb{S}$ is a tuple $s := \langle p_{1}, p_{2}, p_{3}$, $\cdots p_{n} \rangle$, where
\begin{itemize}
  \item p is a visualisation or instance of an user property;
  \item p is not a mental or depression close-related symptom;
  \item n could be an infinite integer so the number of p elements could be unlimited;
  \item all p elements in the same user profile are generally independent.\\
\end{itemize}
}

@@

Generally, we can label the users into two classes: depression users and group away of depression. We naturally employ machine learning technique for classification to seek an effective solution. And the binary classification is seen as a supervised learning because the objective is to use machine learning to automatically classify participants into two labelled categories of depression and depression-less.
\\
\bigskip
\goodbreak

% =================================================================Framework
\section{Framework}
The Framework is the theoretical structure of research study to describe and explain all level models and classification methods. It comprises several modules that establish a completely detailed structure of research study. Implementation of the Framework is the procedure of research experiment. And it explains how the research problem is analysed and in which content the research problem is solved. 
\\

@@

\subsection{Psychological Knowledge Base}
Kroenke et, al. \cite{Kroenke} discovered that there was a strong association between increasing depression severity screen scores and worsening functionality on all 6 categories: mental, social, role, pain, physical and general functions. These 6 categories were directly interpreted 5 items of mental health diagnostic criteria in Mental Health Inventory (MHI-5) and additionally mental disorder symptoms as mental category. The research illustrated graphically the relationship between increasing PHQ-9 scores of depression and worsening functional categories (see Fig.~\ref{fig2}). 
\begin{figure}[h]
\includegraphics[width=1\textwidth]{phq-9.png}
\caption{The relationship between depression severity and personal health-related functionalities\cite{Kroenke}} \label{fig2}
\end{figure}

@@

Data cleaning and transformation is prior in the whole procedure of data preparation because all data should be computer readable and not redundant. And data types in the dataset are justified in order to make each other compatible and comparative. The normalisation is also necessary to uniform the scale condition in various questions. Whilst data preprocessing is implemented, psychological domain knowledge in functional diagnostic criteria is applied in the reconstruction of data structure. According to Definition 4, we can lower the dimension of data set by reducing the number of tables. All tables need to be reconstructed into only six tables referred by six categories of depression diagnostic criteria in functionality (see Fig.~\ref{fig3}).
\begin{figure}[h]
\includegraphics[width=1\textwidth]{restructure.png}
\caption{Data Restructure based on Psychological Knowledge Base} \label{fig3}
\end{figure}
They may involve different number of questions but they all have the same participants. Furthermore, those six tables can be rejoin into one big table due to same row index of them. By instant consideration of those tables, each table forms a new dataset where participants are cases and questions are features. We can therefore define the new datasets after data pre-processing as below:\\
\\
\textbf{Definition 5} Let new overall dataset of m cases and n features $\mathbb{D}_{overall}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, and sub-datasets of different 6 functional categories $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{role}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{physical}$ and $\mathbb{D}_{general}$, where
\begin{itemize}
  \item $|\mathbb{D}_{overall}|$ = $|\mathbb{D}_{mental}|$ = $|\mathbb{D}_{social}|$ = $|\mathbb{D}_{role}|$ = $|\mathbb{D}_{pain}|$ = $|\mathbb{D}_{physical}|$ = $|\mathbb{D}_{general}|$ = $m$;
  \item Feature($\mathbb{D}_{mental}$) + Feature($\mathbb{D}_{social}$) + Feature($\mathbb{D}_{role}$) + Feature($\mathbb{D}_{pain}$) + Feature($\mathbb{D}_{physical}$) + Feature($\mathbb{D}_{general}$) = Feature($\mathbb{D}_{overall}$) = n . \\
\end{itemize}

@@

In this ensemble method, the driving principle is to build a couple of estimators independently and then to average their predictions. The combined estimator is usually better than any of the single base estimator because instances' variance is moderated.
\\
\smallskip

\subsubsection{Algorithm}
Given a well-preprocessed dataset of m examples and n features $\mathbb{D}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, we can generate a suitable ensemble model $\mathbb{M}_{e} $ to present a mapping of $\big\{ x_{1}, x_{2}, ... , x_{n} \big\}$ to $\big\{ y \big\}$ by applying $h$ various types of baseline model $M_{i}$:\\
\IncMargin{1em}
\begin{algorithm}[H]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{Dataset $\mathbb{D}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$}
\Output{Ensemble Model $\mathbb{M}_{e} $}
\BlankLine
Set the training set as $\mathbb{R} = \big\{ (x_{1}, x_{2}, ... , x_{n} ), x_{i} \in R^{m} \big\}$, and the testing set as $\mathbb{S} = \big\{  y, y \in {\{0, 1\}}^{m}  \big\}$\;
\For{$i\leftarrow 1$ \KwTo $h$}{
	\emph{/* validate baseline model */ }\\
	Do training $M_{i}$ on the training set $\mathbb{R}$ \;
	Get the performance $E_{i}$ while validating the training result on $\mathbb{S}$ \;
}
Calculate $w_{i} = \frac{1 - E_{i} }{\sum_{k = 1}^{h} (1 - E_{k}) }$; /* calculate performance weightings */\\
Obtain the ensemble model $\mathbb{M}_{e} = \sum_{g = 1}^{h} w_{i} M_{i} $\;
\caption{Ensemble Modelling}\label{ensemble}
\end{algorithm}\DecMargin{1em}

\subsubsection{Baseline Classification Technique}
Our ensemble classification method involves several baseline supervised classification models. Supervised classification is one of most frequently applications in predictive data mining. We have concentrated on selecting intricate supervised learning algorithms within diverse advantages. The goal of each classification method is to build a concise model to achieve the best possible prediction accuracy. However, each classification method has diverse computing algorithm. There are several most important supervised machine learning techniques \cite{Kotsiantis}:
\begin{enumerate}[label=\alph*)]
	\item Logic based algorithm: The algorithms use logic or rules to make a decision of selecting proper features during the learning. Decision tree method adopts this algorithm.
	\item Perceptron-based techniques: The algorithms are based on the notion of perceptron to construct a pattern like layers of neutrons to learn different paths in the classification. Neutral network is its well-known representer.
	\item Statistical learning algorithms: The algorithm uses statistical approaches to provide a probability that an instance belongs in each class. Under this category of classification algorithms, one can find Naive Bayesian network and k-Nearest Neighbour technique.
	\item Support vector machines: Support Vector Machine is the newest supervised machine learning technique \cite{Kotsiantis}. In classic, it uses a hyperplane to separate two data classes and the margin created by the separating hyperplane indicates how the success of classification is. 
\end{enumerate}
We propose to involve one method of each type in order to present sufficient algorithms in the limited number of sub-models. We thereby select four techniques for baseline models: Decision Tree method, Artificial Neutral Network technique, k-Nearest Neighbour method and Support Vector Machine algorithm.
\\

\textbf{Decision Tree (DT):\\}
Decision trees are logic trees that classify instances by evaluating them based on attributes. Each internal node in a decision tree represents evaluating an attribute in an instance, each branch represents the outcome of evaluation and each leaf node represents a class label. Instances are classified starting at the root node and stop at one leaf node after computing all attributes on the path. Decision tree algorithm is the easiest algorithm and capable of classifying huge datasets \cite{Somvanshi}.
It is simple to understand and interpret. Kotsiantis et, al. \cite{Kotsiantis}addressed that one of the most useful characteristics of decision trees is their comprehensibility, which makes users can easily understand why a decision tree classifies an instance as a specific class label. And decision tree method can make a decision even with little hard data. Somvanshi et, al. \cite{Somvanshi} believed that decision tree algorithm can process the data which contains the missing values and errors. Their research showed that decision tree is able to work very good in the presence of redundant attributes. Likewise, a disadvantage of decision tree method is well-known. The algorithm is unstable that a small change in the data may change the overall look of decision tree. However, decision tree algorithm is still one of the most useful and powerful algorithm in supervised learning. 
\\

@@

Meanwhile, Choudhary and Gianey \cite{Choudhary} stated that every learning algorithm differs according to area of application and no algorithm is more powerful than the other in all scenarios. They concluded that the choice of a suitable algorithm depends on the type of problem and the given data, and the accuracy can be improved by using two or more algorithms together. We therefore comprise above four algorithms into ensemble model for this study.
\\

\bigskip
\goodbreak
% =================================================================Experiment
\section{Experiment}
We employ an ensemble supervised learning experiment to classify depressive users from a rare health survey dataset $\mathbb{H}$. We follow psychological knowledge to reduce the dimension of dataset by split dataset into sub-sets. It will not only benefit the processing of classification but also provide a great opportunity to compare the performance of overall dataset and subsets for support of further solution on the real condition with less features.
\\
\medskip

\subsection{Experiment Design}
In experiment, we first obtain dataset $\mathbb{D}_{overall}$ by data preprocessing on survey data $\mathbb{H}$; next, we aggregate all features of $\mathbb{D}_{overall}$ into 6 health-related functional classes and follow the same procedure to divide $\mathbb{D}_{overall}$ into 6 sub-sets $\mathbb{D}_{physical}$, $\mathbb{D}_{role}$, $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{pain}$ and $\mathbb{D}_{general}$; and we train dataset $\mathbb{D}_{overall}$ by four baseline models (DT, ANN, KNN, SVM) to obtain the relevant performances; then we build the ensemble model $\mathbb{M}_{e}$ by calculating the performance weight $w_{i}$ of each baseline model $M_{i} $; furthermore, we train all 6 sub-datasets by the ensemble classifier $\mathbb{M}_{e}$; and the final step is to use k-fold cross validation algorithm to value the complete predictive performance. The overall look of all experiment proceedings is illustrated in Fig.~\ref{fig4}. 
\begin{figure}[h]
\includegraphics[width=1\textwidth]{experiment.png}
\caption{The overall look of experiment proceedings} \label{fig4}
\end{figure}
\\

From the proceeding details of classification, we can define the algorithm of whole experiment as below: \\
\IncMargin{1em}
\begin{algorithm}[H]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{a rare health survey dataset $\mathbb{H}$}
\Output{Ensemble Classifier $\mathbb{F}_{e}$ and the complete prediction}
\BlankLine
Obtain dataset $\mathbb{D}_{overall}$ by data pre-processing on survey data $\mathbb{H}$\;
Aggregate features manually referred on 6 psychological functionalities \;
Divide $\mathbb{D}_{overall}$ into \{$\mathbb{D}_{physical}$, $\mathbb{D}_{role}$, $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{general}$ \}\;
Supervised learning on $\mathbb{D}_{overall}$ for ensemble model $\mathbb{M}_{e} = \sum_{g = 1}^{h} w_{i} M_{i} $\;
\ForEach{sub-dataset $\mathbb{D}_{i}$ in \{$\mathbb{D}_{overall}, \mathbb{D}_{physical}$, $\mathbb{D}_{role}$, $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{general}$ \}}{
	\emph{/* ensemble classification*/}\\
	Do ensemble classification on  $\mathbb{D}_{i}$ \;
	Validate its predictive performance\;
}
\caption{Experiment Design}\label{experiment}
\end{algorithm}\DecMargin{1em}

>>>>

% =================================================================Abstract
\setlinespacing{1.3}
\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}
Major depressive disorder is a serious worldwide issue for healthcare. This study was to transfer current psychological knowledge on depression diagnosis into an analysis technique of health survey data. It aimed to provide psychologists a proper algorithm for automate screening a large number of samples to identify depressed cases among. The research proposed an effective ensemble binary classifier for distinguishing depressive instances from a wide range of healthcare data. On the experimental evaluation on the NCHS health dataset, it has a significant measure \textbf{0.976} of F1 score in the prediction, without \textbf{any} incorrectly identified depression instance. Only about \textbf{4\%} instances had been mistakenly classified into depressed cases with a significant Accuracy \textbf{95.4\%} comparing to the result from PHQ-9 mental screen inventory. The presented ensemble binary classifier performed comparably better than each baseline algorithms in all measures and all experiment. It approved that the ensemble system is stable and robust to preliminary screening of depressive instances from a large number of health data. In this research, we introduced how to transfer the psychological knowledge into the classification methodology on health dataset. Meanwhile, we analysed the ensemble technique and several supervised learning classification algorithms for building a solid classification method. Finally, we trained the ensemble model on processed dataset, tested and evaluated with the result of mental screen inventory, discussed the comparable predictions, and pointed out the future research directions. 
%
\vspace{1cm}
\\
\textbf{keywords}:  
	major depressive disorder, ensemble classification technique, binary classifier, supervised learning, mental screen inventory, mental diagnostic criteria, psychological knowledge.

@@

Mental disorder is one of the most serious and prevalent healthcare issues worldwide \cite{Wongkoblap}. According to 2012 world health journal by the World Health Organisation (WHO), more than 350 million people have major depressive disorder which can leads to suicide in the worst circumstance. Major depressive disorder also known simply as depression, has been a global challenge for healthcare over years. In psychological domain, it is defined as a mental disorder consistent with at least two weeks of developing low mood across most situations \cite{Zimmerman}. Major depressive disorder can be successfully diagnosed by interviewers normally psychologists, applying operational diagnostic criteria of depression. However, a wide range of depressive patients did not seek clinic advices or professional care at all \cite{Huerta-Ramirez}. Health professionals hence often fail to approach a proper depressive patient at an early stage. 
\\

@@

Therefore, the objective of the present paper is to propose a suitable effective machine learning method in discriminating depression from collected health data for further interview diagnosis. 
\\
\bigskip
\goodbreak
% =================================================================Related-work
\section{Related Work}
\subsection{Psychological Studies Of Screening Depression}
In the domain of psychology, researchers created questionnaire-based scale instruments for roughly screening the mental status of patients. Several measures among them have been widely accepted as good and reliable tools, such as BDI \cite{Huerta-Ramirez}\cite{Tsugawa}, CES-D \cite{De Choudhury}\cite{Tsugawa}, SCL-20 and PHQ-9 \cite{Kroenke}. 
\\

@@

From these two studies on extracting depressive features, the task that aims at establishing a suitable dataset from online social media to predict depression based on extracted features is actually intricate. And there is a lack of machine learning methodology in these researches to automate the proceeding of classifying depression from non-depression.
\\
\medskip
\subsection{Researches Of Classifying Depression}
From various online contents of depressive symptoms and non-depression indicators, it is possible to use machine learning techniques to develop automatic detection systems for major depressive disorders. Unusual actions and uncommon patterns of interaction \cite{Wongkoblap} in social networks can be classified into cases or non-cases of depression through existing learning algorithms,  such as Support Vector Machine algorithm, Naive Bayes method and Random Forest technique.
\\

@@

Despite an increasing number of studies investigating depression using social media data, some common problems persist \cite{Wongkoblap}. Successfully distinguishing depressive users from rich­ data source like social media is problematic, "not only due to biases associated with the collection methods, but also with regard to managing consent and selecting appropriate analytics techniques" \cite{Wongkoblap}. In order to improve the performance of preliminary screening major depressive disorders in a relatively large samples, we need to explore a more suitable and high-quality classification technique for detecting depression.
\\
\bigskip
\goodbreak
% =================================================================Research Problem
\section{Research Problem}
This research aims to design an effective classification method for automatically detecting depressed cases in healthcare dataset and also to provide a solid fundation for future preliminary screening of major depressive disorder on social networks. In order to clearly describe the research, the research objective is defined:\\\\
\textbf{Definition 1} \textit{Let $\mathbb{S}$ be a set of user properties to present an effective user profile for depression, a user property s $\in$ $\mathbb{S}$ is a tuple $s := \langle p_{1}, p_{2}, p_{3}$, $\cdots p_{n} \rangle$, where
\begin{itemize}
  \item p is a visualisation or instance of an user property;
  \item p is not a mental or depression close-related symptom;
  \item n could be an infinite integer so the number of p elements could be unlimited;
  \item all p elements in the same user profile are generally independent.\\
\end{itemize}
}

@@

Generally, we can label the cases waiting for detection into two classes: depression instances and non-depressed examples. We naturally employ machine learning technique for classification to seek an effective solution. And the binary classification is seen as a supervised learning because the objective is to use machine learning to automatically classify participants into two labelled categories of depression and non-depression.
\\
\bigskip
\goodbreak

% =================================================================Framework
\section{Framework}
The Framework is the theoretical structure of research study to describe and explain all level models and classification methods. It comprises several modules that establish a completely detailed structure of research study. Implementation of the Framework is the procedure of research experiment. And it explains how the research problem is analysed and in which content the research problem is solved.

@@

\subsection{Psychological Knowledge}
Kroenke et, al. \cite{Kroenke} discovered that there was a strong association between increasing depression severity screen scores and worsening functionality on all 6 categories: mental, social, role, pain, physical and general functions. These 6 categories were directly interpreted 5 items of mental health diagnostic criteria in Mental Health Inventory (MHI-5) and additionally mental disorder symptoms as mental category. The research illustrated graphically the relationship between increasing PHQ-9 scores of depression and worsening functional categories (see Fig.~\ref{fig2}). 
\begin{figure}[h]
\includegraphics[width=1\textwidth]{phq-9.png}
\caption{The relationship between depression severity and personal health-related functionalities\cite{Kroenke}} \label{fig2}
\end{figure}

@@

Data cleaning and transformation is prior in the whole procedure of data preparation because all data should be computer readable and not redundant. And data types in the dataset are justified in order to make each other compatible and comparative. The normalisation is also necessary to uniform the scale condition in various questions. Whilst data preprocessing is implemented, psychological domain knowledge in functional diagnostic criteria is applied in the reconstruction of data structure. According to Definition 4, we can lower the dimension of data set by reducing the number of tables. All tables need to be reconstructed into only six tables referred by six categories of depression diagnostic criteria in functionality (see Fig.~\ref{fig3}).
\begin{figure}[h]
\hspace{2cm}
\includegraphics[width=0.6\textwidth]{restructure.png}
\caption{Data Restructure based on Psychological Knowledge Base} \label{fig3}
\end{figure}
They may involve different number of questions but they all have the same participants. Furthermore, those six tables can be rejoin into one big table due to same row index of them. By instant consideration of those tables, each table forms a new dataset where participants are cases and questions are features. We can therefore define the new datasets after data pre-processing as below:\\
\\
\textbf{Definition 5} Let new overall dataset of m cases and n features $\mathbb{D}_{overall}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, and sub-datasets of different 6 functional categories $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{role}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{physical}$ and $\mathbb{D}_{general}$, where
\begin{itemize}
  \item $|\mathbb{D}_{overall}|$ = $|\mathbb{D}_{mental}|$ = $|\mathbb{D}_{social}|$ = $|\mathbb{D}_{role}|$ = $|\mathbb{D}_{pain}|$ = $|\mathbb{D}_{physical}|$ = $|\mathbb{D}_{general}|$ = $m$;
  \item Feature($\mathbb{D}_{mental}$) + Feature($\mathbb{D}_{social}$) + Feature($\mathbb{D}_{role}$) + Feature($\mathbb{D}_{pain}$) + Feature($\mathbb{D}_{physical}$) + Feature($\mathbb{D}_{general}$) = Feature($\mathbb{D}_{overall}$) = n . \\
\end{itemize}

@@

In this ensemble method, the driving principle is to build a couple of estimators independently and then to average their predictions. The combined estimator is usually better than any of the single base estimator because instances' variance is moderated.

\subsubsection{Algorithm}
Given a well-preprocessed dataset of m examples and n features $\mathbb{D}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, we can generate a suitable ensemble model $\mathbb{M}_{e} $ to present a mapping of $\big\{ x_{1}, x_{2}, ... , x_{n} \big\}$ to $\big\{ y \big\}$ by applying $h$ various types of baseline model $M_{i}$:\\
\IncMargin{2em}
\begin{algorithm}[H]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{Dataset $\mathbb{D}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$}
\Output{Ensemble Model $\mathbb{M}_{e} $}
\BlankLine
Set the training set as $\mathbb{R} = \big\{ (x_{1}, x_{2}, ... , x_{n} ), x_{i} \in R^{m} \big\}$, and the testing set as $\mathbb{S} = \big\{  y, y \in {\{0, 1\}}^{m}  \big\}$\;
\For{$i\leftarrow 1$ \KwTo $h$}{
	\emph{/* validate baseline model */ }\\
	Do training $M_{i}$ on the training set $\mathbb{R}$ \;
	Get the performance $E_{i}$ while validating training result on $\mathbb{S}$ \;
}
Calculate $w_{i} = \frac{1 - E_{i} }{\sum_{k = 1}^{h} (1 - E_{k}) }$; /* calculate performance weightings */\\
Obtain the ensemble model $\mathbb{M}_{e} = \sum_{g = 1}^{h} w_{i} M_{i} $\;
\caption{Ensemble Modelling}\label{ensemble}
\end{algorithm}\DecMargin{2em}

\subsubsection{Baseline Classification Technique}
Our ensemble classification method involves several baseline supervised classification models. Supervised classification is one of most frequently applications in predictive data mining. We have concentrated on selecting intricate supervised learning algorithms within diverse advantages. The goal of each classification method is to build a concise model to achieve the best possible prediction accuracy. However, each classification method has diverse computing algorithm. There are several most important supervised machine learning techniques \cite{Kotsiantis}:\\
\begin{enumerate}[label=\alph*)]
	\item Logic based algorithm: The algorithms use logic or rules to make a decision of selecting proper features during the learning. Decision tree method adopts this algorithm.
	\item Perceptron-based techniques: The algorithms are based on the notion of perceptron to construct a pattern like layers of neutrons to learn different paths in the classification. Neutral network is its well-known representer.
	\item Statistical learning algorithms: The algorithm uses statistical approaches to provide a probability that an instance belongs in each class. Under this category of classification algorithms, one can find Naive Bayesian network and k-Nearest Neighbour technique.
	\item Support vector machines: Support Vector Machine is the newest supervised machine learning technique \cite{Kotsiantis}. In classic, it uses a hyperplane to separate two data classes and the margin created by the separating hyperplane indicates how the success of classification is. \\
\end{enumerate}

We propose to involve one method of each type in order to present sufficient algorithms in the limited number of sub-models. We thereby select four techniques for baseline models: Decision Tree method, Artificial Neutral Network technique, k-Nearest Neighbour method and Support Vector Machine algorithm.
\\

\textbf{Decision Tree (DT):\\}
Decision trees are logic trees that classify instances by evaluating them based on attributes. Each internal node in a decision tree represents evaluating an attribute in an instance, each branch represents the outcome of evaluation and each leaf node represents a class label. Instances are classified starting at the root node and stop at one leaf node after computing all attributes on the path. Decision tree algorithm is the easiest algorithm and capable of classifying huge datasets \cite{Somvanshi}.
It is simple to understand and interpret. Kotsiantis et, al. \cite{Kotsiantis}addressed that one of the most useful characteristics of decision trees is their comprehensibility, which makes users can easily understand why a decision tree classifies an instance as a specific class label. And decision tree method can make a decision even with little hard data. Somvanshi et, al. \cite{Somvanshi} believed that decision tree algorithm can process the data which contains the missing values and errors. Their research showed that decision tree is able to work very good in the presence of redundant attributes. Likewise, a disadvantage of decision tree method is well-known. The algorithm is unstable that a small change in the data may change the overall look of decision tree. However, decision tree algorithm is still one of the most useful and powerful algorithm in supervised learning. 
\\\\\\

@@

Meanwhile, Choudhary and Gianey \cite{Choudhary} stated that every learning algorithm differs according to area of application and no algorithm is more powerful than the other in all scenarios. They concluded that the choice of a suitable algorithm depends on the type of problem and the given data, and the accuracy can be improved by using two or more algorithms together. We therefore comprise above four algorithms into ensemble model for this study.
\\
\\
\\

\bigskip
\goodbreak
% =================================================================Experiment
\section{Experiment}
We employ an ensemble supervised learning experiment to classify depressive users from a rare health survey dataset $\mathbb{H}$. We follow psychological knowledge to reduce the dimension of dataset by split dataset into sub-sets. It will not only benefit the processing of classification but also provide a great opportunity to compare the performance of overall dataset and subsets for support of further solution on the real condition with less features.

\subsection{Experiment Design}
In experiment, we first obtain dataset $\mathbb{D}_{overall}$ by data preprocessing on survey data $\mathbb{H}$; next, we aggregate all features of $\mathbb{D}_{overall}$ into 6 health-related functional classes and follow the same procedure to divide $\mathbb{D}_{overall}$ into 6 sub-sets $\mathbb{D}_{physical}$, $\mathbb{D}_{role}$, $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{pain}$ and $\mathbb{D}_{general}$; and we train dataset $\mathbb{D}_{overall}$ by four baseline models (DT, ANN, KNN, SVM) to obtain the relevant performances; then we build the ensemble model $\mathbb{M}_{e}$ by calculating the performance weight $w_{i}$ of each baseline model $M_{i} $; furthermore, we train all 6 sub-datasets by the ensemble classifier $\mathbb{M}_{e}$; and the final step is to use k-fold cross validation algorithm to value the complete predictive performance. The overall look of all experiment proceedings is illustrated in Fig.~\ref{fig4}. 
\begin{figure}[h]
\includegraphics[width=1\textwidth]{experiment.png}
\caption{The overall look of experiment proceedings} \label{fig4}
\end{figure}
\\
\\

From the proceeding details of classification, we can define the algorithm of whole experiment as below: \\\\\\
\IncMargin{2em}
\begin{algorithm}[H]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{a rare health survey dataset $\mathbb{H}$}
\Output{Ensemble Classifier $\mathbb{F}_{e}$ and the complete prediction}
\BlankLine
Obtain dataset $\mathbb{D}_{overall}$ by data pre-processing on survey data $\mathbb{H}$\;
Aggregate features manually referred on 6 psychological functionalities \;
Divide $\mathbb{D}_{overall}$ into \{$\mathbb{D}_{physical}$, $\mathbb{D}_{role}$, $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{general}$ \}\;
Supervised learning on $\mathbb{D}_{overall}$ for ensemble model $\mathbb{M}_{e} = \sum_{g = 1}^{h} w_{i} M_{i} $\;
\ForEach{sub-dataset $\mathbb{D}_{i}$ in \{$\mathbb{D}_{overall}, \mathbb{D}_{physical}$, $\mathbb{D}_{role}$, $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{general}$ \}}{
	\emph{/* ensemble classification*/}\\
	Do ensemble classification on  $\mathbb{D}_{i}$ \;
	Validate its predictive performance\;
}
\caption{Experiment Design}\label{experiment}
\end{algorithm}\DecMargin{2em}

\bigskip
\bigskip
The ensemble classification can be expressed in algorithm as well: Given a well-preprocessed dataset of m examples and n features $\mathbb{D}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, we can obtain the ensemble classifier $\mathbb{F}_{e}$ = $w_{svm} \cdot f_{svm}$ + $w_{nb} \cdot f_{nb}$ + $w_{knn} \cdot f_{knn}$ + $w_{dt} \cdot f_{dt}$ by applying supervised learning on dataset $\mathbb{D}$:\\
\IncMargin{2em}
\begin{algorithm}[H]
\SetKwFunction{Median}{Median}
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{Dataset $\mathbb{D}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$}
\Output{the optimised ensemble classifier $\mathbb{F}_{e} $ and its predictive performance $p_{e}$ }
\BlankLine
Divide dataset $\mathbb{D}$ into k portions, each portion has $\frac{m}{k}$ examples\;
\For{$k\leftarrow 1$ \KwTo 5}{ 
	Select all portions except $k^{th}$ portion to form new dataset $\mathbb{D}^{'}$ \;
	Use $\mathbb{D}^{'}$ to generate the training set $\mathbb{R} = \big\{ (x_{1}, x_{2}, ... , x_{n} ) \big\}$ and the testing set $\mathbb{S} = \big\{  y \big\}$, where $|\mathbb{D}^{'}| = |\mathbb{R}| = |\mathbb{S}| = \frac{4}{5}|\mathbb{D}| = \frac{4m}{5}$\;
	\emph{/* baseline model */}\\
	\ForEach{ one classification method of SVM, ANN, KNN, DT}{ 
		Training on the training set $\mathbb{R}$ and obtain classifier $f$\;
		 Obtain predictive value $y^{p} = f(\sum_{i=1}^{n} (x_{i}))$ \;
	}
	\emph{/* ensemble */}\\
	Calculate the ensemble classifier $\mathbb{F}_{k}$ = $w_{svm} \cdot f_{svm}$ + $w_{nb} \cdot f_{nb}$ + $w_{knn} \cdot f_{knn}$ + $w_{dt} \cdot f_{dt}$ \;
	Calculate a float predictive value $y_{e}$ = $w_{svm} \cdot y_{svm}^{p}$ + $w_{nb} \cdot y_{nb}^{p}$ + $w_{knn} \cdot y_{knn}^{p}$ +$w_{dt} \cdot y_{dt}^{p}$ \;
	\emph{/* sensitivity */}\\
	\eIf{$y_{e} > 0.5$}{
		$y_{e} = 1$ \emph{/* non-depression */}
	}{
		$y_{e} = 0$ \emph{/* depression */}
	}
	Test $y_{e}$ on testing set $\mathbb{S}$ and report predictive performance $p_{k}$ \;
}
\emph{/* 5-fold cross validation */}\\
Validate the predictive performance by calculating $\displaystyle p_{e} = \frac{\sum_{k=1}^{5} p_{k}}{5}$ \;
Generate the optimised ensemble classifier \hspace{6cm} $\mathbb{F}_{e}$ = Median($\mathbb{F}_{1}, \mathbb{F}_{2}, \mathbb{F}_{3}, \mathbb{F}_{4}, \mathbb{F}_{5}$)
\caption{Ensemble Classification Procedure}\label{classification}
\end{algorithm}\DecMargin{2em}
\medskip
